### 2018-06-07 1_intro.tex
Consider final Professor's comments.
itmo: remove footnotes.

The very first tool that performs the WMM-aware portability analysis is \porthos{}%
%
\footnote{The \porthos{} project web site: \url{http://github.com/hernanponcedeleon/Dat3M}} %
%
introduced in April~2017~\cite{Porthos17a}.
This tool reduces described problem to a bounded reachability problem, which can be solved via an SMT-solver (see Section~\ref{ch:enc:bmc}).
This approach allows to capture symbolically the semantics of analysing program and both weak memory models into a single SMT-formula, augmented by the reachability assertion.
As most modern SMT-solvers are efficient enough to be able to operate the state space of size millions of variables bounded by millions of constraints~(\cite{malik2009boolean}), the used method can be applicable in solving the real-world problems.
% about SAT: https://courses.cs.washington.edu/courses/csep573/11wi/lectures/ashish-satsolvers.pdf

@@

The thesis is organised as following.
Chapter~\ref{ch:wmm} gives a general view on the weak memory model-aware analysis.
Chapter~\ref{ch:enc} examines the portability analysis as an bounded reachability problem that can be encoded into an SMT-formula in order to be solved automatically by an SMT~solver.
Chapter~\ref{ch:impl} delves into the description of architectural solutions and implementation details of the \porthos[2] framework.
Chapter~\ref{ch:eval} gives a comparison of key features of \porthos[2] and \porthos[1] by providing examples of the compilation and the unrolling stages; and it provides some performance benchmarks of \porthos[2] in both reachability and portability analysis modes.
Chapter~\ref{ch:summary} summarises results of the work and proposes possible directions of the future work.

>>>>

The very first tool that performs the WMM-aware portability analysis is \porthos{}%
%
\footnote{The \porthos{} project repository: \url{http://github.com/hernanponcedeleon/Dat3M}} %
%
introduced in April~2017~\cite{Porthos17a}.
This tool reduces described problem to a bounded reachability problem, which can be solved via an SMT-solver (see Section~\ref{ch:enc:bmc}).
This approach allows to capture symbolically the semantics of analysing program and both weak memory models into a single SMT-formula, augmented by the reachability assertion.
As most modern SMT-solvers are efficient enough to be able to operate the state space of size millions of variables bounded by millions of constraints~(\cite{malik2009boolean}), the used method can be applicable in solving the real-world problems.
% about SAT: https://courses.cs.washington.edu/courses/csep573/11wi/lectures/ashish-satsolvers.pdf

@@

The thesis is organised as following.
Chapter~\ref{ch:wmm} gives a general view on the weak memory model-aware analysis.
Chapter~\ref{ch:enc} examines the portability analysis as an bounded reachability problem that can be encoded into an SMT-formula in order to be solved automatically by an SMT~solver.
Chapter~\ref{ch:impl} delves into the description of architectural solutions and implementation details of the \porthos[2] framework.
Chapter~\ref{ch:eval} gives a comparison of key features of \porthos[2] and \porthos[1] by providing examples of the compilation and the unrolling stages; and it provides some performance benchmarks of \porthos[2] in both reachability and portability analysis modes.
Chapter~\ref{ch:summary} summarises results of the work and proposes possible directions for future work.

### 2018-06-07 5_eval.tex
itmo: remove footnotes.

As another example of program liable for analysis consider the Dekker's algorithm for mutual exclusion of two processes, originally described by Dijkstra~\cite{dijkstra1962over}; the program is presented in Appendix~\ref{apx:dekker}.
For testing \porthos[1], we used the same file in old \porthos{} input language (\texttt{dekker.pts}), which was used in evaluation tests in the original paper~\cite{Porthos17a}.
For performing tests, \porthos[2] was slightly modified in the branch \textit{ay/test-timing}%
\footnote{The modifications were pushed into the \porthos[1] repository \url{github.com/hernanponcedeleon/Dat3M}} %
%
for printing detailed timing information and statistics about number of events (commit f8a6c97f) and writing this information in strict \textit{json} format so that it can be easily processed later by a script that analyses and prints the results (commit 48ba7161).
The version of \porthos[2] used for the tests is actual up to commit 01dde6b1 of the \porthos[2] repository%
\footnote{\porthos[2] repository: \url{https://github.com/ajuszkowski/PorthosC}}. %
%
Both \porthos[1] and \porthos[2] are run in the state reachability mode for TSO memory model (see sample output of \porthos[2] in Appendix~\ref{apx:output}).

>>>>

As another example of program liable for analysis consider the Dekker's algorithm for mutual exclusion of two processes, originally described by Dijkstra~\cite{dijkstra1962over}; the program is presented in Appendix~\ref{apx:dekker}.
For testing \porthos[1], we used the same file in old \porthos{} input language (\texttt{dekker.pts}), which was used in evaluation tests in the original paper~\cite{Porthos17a}.
For performing tests, \porthos[2] was slightly modified in the branch \textit{ay/test-timing}%
\footnote{The modifications were pushed into the \porthos[1] repository \url{github.com/hernanponcedeleon/Dat3M}} %
%
for printing detailed timing information and statistics about number of events (commit f8a6c97f) and writing this information in strict \textit{json} format so that it can be easily processed later by a script that analyses and prints the results (commit 48ba7161).
The version of \porthos[2] used for the tests is actual up to commit 01dde6b1 of the \porthos[2] GitHub repository.
Both \porthos[1] and \porthos[2] are run in the state reachability mode for TSO memory model (see sample output of \porthos[2] in Appendix~\ref{apx:output}).
